---
title: "p8105_hw1_sr4354"
author: "sr4354"
date: "2026-09-25"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

## problem 1

The penguins dataset contains data on penguins from three islands in Antarctica. There are `r nrow(penguins)` rows and `r ncol(penguins)` columns, and each row is one penguin. The variables include `species` (`r levels(penguins$species)`), `island` (`r levels(penguins$island)`), `sex` (`r levels(penguins$sex)`), and  `year` (ranging from `r range(penguins$year, na.rm = TRUE)`), along with some physical measurements: bill length, bill depth, flipper length, and body mass. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm, and the mean bill length is `r mean(penguins$bill_length_mm, na.rm = TRUE)` mm.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()
ggsave("flipper_vs_bill.png")
```

