---
title: "p8105_hw1_sr4354"
author: "sr4354"
date: "2026-09-25"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

## problem 1

The penguins dataset contains data on penguins from three islands in Antarctica. There are `r nrow(penguins)` rows and `r ncol(penguins)` columns, and each row is one penguin. The variables include `species` (`r levels(penguins$species)`), `island` (`r levels(penguins$island)`), `sex` (`r levels(penguins$sex)`), and  `year` (ranging from `r range(penguins$year, na.rm = TRUE)`), along with some physical measurements: bill length, bill depth, flipper length, and body mass. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm, and the mean bill length is `r mean(penguins$bill_length_mm, na.rm = TRUE)` mm.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()
ggsave("flipper_vs_bill.png")
```

## problem 2

```{r}
normal_sample = rnorm(10)
is_positive = normal_sample > 0
flowers_vec = c("lotus", "jasmine", "rose", "lily", "daffodil", "pansy", "sunflower", "marigold", "poppy", "peony")
frequency_factor = factor(c("rarely", "sometimes", "always", "rarely", "sometimes", "always", "rarely", "sometimes", "always", "rarely"))

my_df = data.frame(
  normal_sample = normal_sample,
  is_positive = is_positive,
  flowers_vec = flowers_vec,
  frequency_factor = frequency_factor
)
```

```{r}
my_df |> pull(normal_sample) |> mean()
my_df |> pull(is_positive) |> mean()
my_df |> pull(flowers_vec) |> mean()
my_df |> pull(frequency_factor) |> mean()
```

```{r, eval=FALSE}
as.numeric(my_df$is_positive)
as.numeric(my_df$flowers_vec)
as.numeric(my_df$frequency_factor)
```

For is_positive, TRUE becomes 1 and FALSE becomes 0, so taking the mean gives a meaningful number (the proportion of TRUE values). For flowers_vec, R cannot coerce words into numbers, so every value becomes NA. For frequency_factor, as.numeric() doesn't say anything meaningful about the frequencies because it assigns numbers to the levels based on alphabetical order, so the mean could not be calculated.
